Four decades of water quality change in the upper San Francisco Estuary

### 2017-01-10 sftrends_manu.Rnw
fixed theme issues in p8trnd

@@

What about flow? \cref{fig:dinc10}, \cref{fig:dinc10dyna}

@@

Estimated annual percent change of ammonium from 1976-1995 at P8 was more than twice that shown in Ref.~\citenum{Jabusch16}, suggesting that flow effects on the time series lead to an under-estimate of the actual change. \cref{tab:trnds} shows an approximate 5\% increase per year, compared to 2\% in Fig 2 from Ref.~\citenum{Jabusch16}.  Mid-1990s was high flow, which diluted the observed ammonium and removal of this component showed a steady, positive increase in the flow-normalized trend (\cref{fig:p8trnds}).

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,page=1]{figs/trndcomp1.pdf}
\caption{Results from seasonal Kendall tests on model predictions from \ac{wrtds}. Trends were evaluated using predicted (triangles) and flow-normalized (circles) results to identify potential effects of flow. Results are the estimated direction and magnitude of the trend ($\tau$, varying from -1 to 1 with significance at $\alpha = 0.05$). Trends are shown separately for different annual groupings. See \cref{fig:trndcomp2,fig:trndcomp3} for seasonal groupings.}
\label{fig:trndcomp1}   
\end{figure}

@@

# globals
ylab1 <- expression(paste(NO [2] ^ '-', ' / ', NO [3] ^ '2-', ' (mg ', L^-1, ')'))
ylab2 <- expression(paste(NH [4] ^ '+', ' (mg ', L^-1, ')'))
flolab <- expression(paste('ln-Flow (', m^3, ' ', s^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm")
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Blues')[c(9, 8, 7)]
dynacol_vec <- RColorBrewer::brewer.pal(9, 'Spectral')
xlims <- range(nomod$date)

# observed time series
toplo1 <- select(nomod, date, res) %>% 
  na.omit()
toplo2 <- select(nhmod, date, res) %>% 
  na.omit()
lndate <- as.Date('2006/01/01')
p1 <- ggplot(toplo1, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  geom_label_repel(
    data = data.frame(x = lndate, y = 35), 
    aes(x, y, label = 'WWTP upgrades'), 
    box.padding = grid::unit(2, "lines"), 
    nudge_x = 1
    ) + 
  scale_x_date(limits = xlims) 
p2 <- ggplot(toplo2, aes(x = date, y = exp(res))) + 
  geom_line() + 
  ptheme + 
  scale_y_continuous(ylab2) +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  geom_label_repel(
    data = data.frame(x = lndate, y = 35), 
    aes(x, y, label = 'WWTP upgrades'), 
    box.padding = grid::unit(2, "lines"), 
    nudge_x = 1
    ) + 
  scale_x_date(limits = xlims)

# prdnrmplots
p3 <- prdnrmplot(nomod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    legend.position = 'top', 
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  scale_x_date(limits = xlims) 
pleg1 <- g_legend(p3)
p3 <- p3 + theme(legend.position = 'none')
p4 <- prdnrmplot(nhmod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  ptheme + 
  scale_y_continuous(ylab2) +
  theme(
    legend.position = 'none',
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  ) +
  scale_x_date(limits = xlims)

# dynaplots
p5 <- dynaplot(nomod, logspace = F, col_vec = dynacol_vec, month = c(1, 4, 7, 10), floscl = F) + 
  ptheme + 
  scale_y_continuous(ylab1) +
  theme(
    legend.position = 'top', 
    legend.title = element_blank()
  ) +
  scale_x_continuous(flolab) + 
  guides(colour = guide_colourbar(barheight = 0.5, barwidth = 10))
pleg2 <- g_legend(p5)
p5 <- p5 + theme(legend.position = 'none')
p6 <- dynaplot(nhmod, logspace = F, col_vec = dynacol_vec, month = c(1, 4, 7, 10), floscl = F) + 
  ptheme + 
  scale_y_continuous(ylab2) +
  scale_x_continuous(flolab) +
  theme(
    legend.position = 'none', 
    legend.title = element_blank()
  )

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,page=1]{figs/trndcomp2.pdf}
\caption{Results from seasonal Kendall tests on model predictions from \ac{wrtds}. Trends were evaluated using predicted (triangles) and flow-normalized (circles) results to identify potential effects of flow. Results are the estimated direction and magnitude of the trend ($\tau$, varying from -1 to 1 with significance at $\alpha = 0.05$). Trends are shown separately for different seasonal groupings from 1976-1995. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. See \cref{fig:trndcomp1} for annual comparisons.}
\label{fig:trndcomp2}   
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\textwidth,page=1]{figs/trndcomp3.pdf}
\caption{Results from seasonal Kendall tests on model predictions from \ac{wrtds}. Trends were evaluated using predicted (triangles) and flow-normalized (circles) results to identify potential effects of flow. Results are the estimated direction and magnitude of the trend ($\tau$, varying from -1 to 1 with significance at $\alpha = 0.05$). Trends are shown separately for different seasonal groupings from 1996-2013. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. See \cref{fig:trndcomp1} for annual comparisons.}
\label{fig:trndcomp3}   
\end{figure}

>>>>

obs_sm <- group_by(delt_dat, Site_Code)
@

@@

What about flow? \cref{fig:dinc10}

@@

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,page=1]{figs/trndcomp1.pdf}
\caption{Results from seasonal Kendall tests on observed data (triangles) and flow-normalized predictions (circles) from \ac{wrtds} for nitrogen analytes. Results are the estimated direction and magnitude of the trend ($\tau$, varying from -1 to 1 with significance at $\alpha = 0.05$). Trends are shown separately for different annual groupings. See \cref{fig:trndcomp2,fig:trndcomp3} for seasonal groupings.}
\label{fig:trndcomp1}   
\end{figure}

@@

# globals
ylab1 <- expression(paste(NO [2] ^ '-', ' / ', NO [3] ^ '2-', ' (mg ', L^-1, ')'))
ylab2 <- expression(paste(NH [4] ^ '+', ' (mg ', L^-1, ')'))
flolab <- expression(paste('ln-Flow (', m^3, ' ', s^-1, ')'))
ptheme <- theme_minimal() +
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"),
    plot.margin = grid::unit(c(6, 6, 0, 6), 'pt')
  )

col_vec <- RColorBrewer::brewer.pal(9, 'Blues')[c(9, 8, 7)]
dynacol_vec <- RColorBrewer::brewer.pal(9, 'Spectral')
xlims <- range(nomod$date)

# observed time series
toplo1 <- select(nomod, date, res) %>% 
  na.omit()
toplo2 <- select(nhmod, date, res) %>% 
  na.omit()
p1 <- ggplot(toplo1, aes(x = date, y = exp(res))) + 
  geom_line() + 
  scale_x_date(limits = xlims) +
  scale_y_continuous(ylab1) +
  ptheme %+replace%
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank()
    )
p2 <- ggplot(toplo2, aes(x = date, y = exp(res))) + 
  geom_line() +
  scale_x_date(limits = xlims) +
  scale_y_continuous(ylab2) +
  ptheme %+replace% 
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank()
    )

# prdnrmplots
p3 <- prdnrmplot(nomod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  scale_x_date(limits = xlims) +
  scale_y_continuous(ylab1) +
  ptheme %+replace% 
  theme(
    legend.position = 'top', 
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )
pleg1 <- g_legend(p3)
p3 <- p3 + 
  ptheme %+replace% 
  theme(
    legend.position = 'none', 
    axis.title.x = element_blank()
    )
p4 <- prdnrmplot(nhmod, logspace = F, col_vec = col_vec, min_mo = 10) + 
  scale_x_date(limits = xlims) +
  scale_y_continuous(ylab2) +
  ptheme %+replace% 
  theme(
    legend.position = 'none',
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )

# dynaplots
p5 <- dynaplot(nomod, logspace = F, col_vec = dynacol_vec, month = c(1, 4, 7, 10), floscl = F) + 
  scale_x_continuous(flolab) + 
  scale_y_continuous(ylab1) +
  ptheme %+replace% 
  theme(
    legend.position = 'top', 
    legend.title = element_blank()
  ) +
  guides(colour = guide_colourbar(barheight = 0.5, barwidth = 10))
pleg2 <- g_legend(p5)
p5 <- p5 + ptheme %+replace% theme(legend.position = 'none')
p6 <- dynaplot(nhmod, logspace = F, col_vec = dynacol_vec, month = c(1, 4, 7, 10), floscl = F) + 
  scale_x_continuous(flolab) +
  scale_y_continuous(ylab2) +
  ptheme %+replace% 
  theme(
    legend.position = 'none', 
    legend.title = element_blank()
  )

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,page=1]{figs/trndcomp2.pdf}
\caption{Results from seasonal Kendall tests on observed data (triangles) and flow-normalized predictions (circles) from \ac{wrtds} for nitrogen analytes. Results are the estimated direction and magnitude of the trend ($\tau$, varying from -1 to 1 with significance at $\alpha = 0.05$). Trends are shown separately for different seasonal groupings from 1976-1995. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. See \cref{fig:trndcomp1} for annual comparisons.}
\label{fig:trndcomp2}   
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\textwidth,page=1]{figs/trndcomp3.pdf}
\caption{Results from seasonal Kendall tests on observed data (triangles) and flow-normalized predictions (circles) from \ac{wrtds} for nitrogen analytes. Results are the estimated direction and magnitude of the trend ($\tau$, varying from -1 to 1 with significance at $\alpha = 0.05$). Trends are shown separately for different seasonal groupings from 1996-2013. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. See \cref{fig:trndcomp1} for annual comparisons.}
\label{fig:trndcomp3}   
\end{figure}
